---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
## Loading and preprocessing the data
```{r loaddata}
setwd("~/Rfiles")
unzip("./RepData_PeerAssessment1/activity.zip", exdir="./RepData_PeerAssessment1/ActivityData")
actData <- read.csv("./RepData_PeerAssessment1/ActivityData/activity.csv")
actDataClean <- na.omit(actData)                   
```
As-01,10-08, 11-01, 11-04, 11-09, 11-10, 11-14 and 11-30 contain only NA values for 
steps taken, these dates are excluded from the dataset. 

## What is mean total number of steps taken per day?
```{r mean}
x <- ddply(actData,~date,summarise,totalSteps=sum(steps))
mean(x$sum)
median(x$sum)
print(x)
```
## What is the average daily activity pattern?
```{r avgdaily, echo=FALSE}
hist(x$sum)
y <- ddply(actDataClean,~interval,summarise,AvgSteps=mean(steps))
plot(y, type="l")
which.max(y$AvgSteps)
```
## Imputing missing values
```{r impute}
actDataFull <- actData
actDataFull[is.na(actDataFull)] <- mean(y$AvgSteps)
```
Replaced all missing values with the mean for all intervals. 

summary(actData)
2304 NAs 

z <- ddply(actDataFull,~date,summarise,totalSteps=sum(steps))
mean(z$totalSteps)
median(z$totalSteps)
hist(z$totalSteps)

Did not affect the mean, though it did make the median equivalent to the mean.  As a result, the distribution of the imputed data looks more normally distributed. 

## Are there differences in activity patterns between weekdays and weekends?
actDataFull$date <- as.POSIXct(actDataFull$date)
actDataFull$Day <- weekdays(actDataFull$data)
plot(interval~steps, type="l", data=)

