---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
## Loading and preprocessing the data
```{r loaddata}
setwd("~/Rfiles")
unzip("./RepData_PeerAssessment1/activity.zip", exdir="./RepData_PeerAssessment1/ActivityData")
actData <- read.csv("./RepData_PeerAssessment1/ActivityData/activity.csv")
actDataClean <- na.omit(actData)                   
```
As-01,10-08, 11-01, 11-04, 11-09, 11-10, 11-14 and 11-30 contain only NA values for 
steps taken, these dates are excluded from the dataset "actDataClean". 

## What is mean total number of steps taken per day?
```{r mean}
library(plyr)
x <- ddply(actData,~date,summarise,totalSteps=sum(steps))
mean(na.omit(x$totalSteps))
median(na.omit(x$totalSteps))
print(x)
```
## What is the average daily activity pattern?
```{r avgdaily}
hist(x$totalSteps)
y <- ddply(actDataClean,~interval,summarise,AvgSteps=mean(steps))
plot(y, type="l")
y$interval[[which.max(y$AvgSteps)]]
```
Interval 835 has the highest average steps value, seen clearly in the line graph above cresting over 200 steps. 

## Imputing missing values
```{r countNA}
summary(actData)
```
There are 2304 NAs in the Dataset.  
```{r impute}
actDataFull <- actData
actDataFull[is.na(actDataFull)] <- mean(y$AvgSteps)
```
Replaced all missing values with the mean for all intervals, about 37. 
  
```{r ImputedAnalysis}
z <- ddply(actDataFull,~date,summarise,totalSteps=sum(steps))
mean(z$totalSteps)
median(z$totalSteps)
hist(z$totalSteps)
```

Imputing the missing values by replacing them with the interval mean did not affect the mean, though it did make the median equivalent to the mean.  As a result, the distribution of the imputed data looks more normally distributed. 

## Are there differences in activity patterns between weekdays and weekends?
```{r weekdays}
actDataFull$date <- as.POSIXct(actDataFull$date)
actDataFull$Day <- factor(weekdays(actDataFull$date))
actDataFull$Day <- revalue(actDataFull$Day, c("Friday"="Weekday", "Monday"="Weekday", "Thursday"="Weekday", "Tuesday"="Weekday", "Wednesday"="Weekday", "Saturday"="Weekend", "Sunday"="Weekend"))
```

```{r plotData, fig.width=10}
ab <- ddply(actDataFull,.(Day, interval),summarise,AvgSteps=mean(steps))
library(ggplot2)
g <- ggplot(ab, aes(interval, AvgSteps))
g + geom_line() + facet_grid(.~Day) + geom_line(stat = "hline", yintercept = "mean", col="red")
```


At first glance, weekdays appear to have a larger number of steps, however, we can see that the mean steps taken is slightly higher on wekeends.  It appears that a single high average value is pushing weeekday steps higher. Perhaps this is a morning walk to work that doesn't occur on weekends? 
